{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-27 wacv_for_review.tex
References updated with ECO, CCOT and SCT

\begin{algorithm*}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$,\\
	Update $R_{t}^{L}$\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm*}

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
the activations of $2^{th}$ convolutional layer features
of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
since it provides higher spatial resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

>>>>

\begin{algorithm*}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	Skip it for $R_{t}^{L}$ (Condition 2) and $R_{t}^{S}$ (Condition 3), $\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$ (Condition 3),\\
	Update $R_{t}^{L}$ (Condition 2),\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm*}

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features in tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to increased translational invariance in this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
the activations of $2^{th}$ convolutional layer features
of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
since it provides higher spatial resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.
